### 2014-11-22 docs/ms.Rmd
Integrated Zurek's edits, but it's changed a fair bit since then

To determine the current state of methods reporting in the field we searched for papers from 2013 in 22 top colour science journals (_Animal Behaviour_, _Behavioral Ecology_, _Journal of Experimental Biology_, _Biology Letters_, _Proceedings of the Royal Society B: Biological Sciences_, _Biological Journal of the Linnean Society_, _Ethology_, _The American Naturalist_, _Ecology Letters_, _Journal of Evolutionary Biology_, _American Journal of Botany_, _Ecology and Evolution_, _Oikos_, _Ecology_, _Journal of Ecology_, _Behavioral Ecology and Sociobiology_, _Current Zoology_, _Naturwissenschaften_, _New Phytologist_, _PLoS ONE_, _Evolution_, _Functional Ecology_). For each of the journals, we used the Boolean search terms 'colour*', 'color*' or 'spectra*' and searched for these in the title or abstract from each of the journal home pages. We read the titles and abstracts of each paper and included only those papers that explicitly used either a spectrophotometer or camera to quantify colour signals. We excluded papers that were: 1) review papers; 2) methodological papers; 3) papers quantifying colour pattern rather than characteristics of each individual colour patch; and 4) papers taking microspectrophotometric measurments of retinal absorbance. To review the large number of papers returned from the searches, journals were haphazardly divided up between the authors. In order to reduce the risk of observer bias in our scoring, papers were read and reassessed by a total of three authors. Any discrepancies between the assessor scores were discussed and agreed upon prior to analysis. We then tabulated what details of the methods were reported against our criteria. The data along with analysis script can be found at: https://github.com/daniel1noble/colsci_rep (TODO: GIVE IT A DOI?). We have kept the papers used in our dataset annoymous to avoid accusing specific colleagues of inadvertant reporting. We feel that the issue of reporting is something attributable to the ambiguity and lack of guidelines in our field and not something specific to individual research groups.

@@

While some of the values reported above seem alarming, it is important to note that papers often made reference to previous work for various methods (`r round(ref_stud, digits = 2)`%), so these figures are slightly liberal given that referenced work may have comprehensively covered some of these criteria. Despite this, many of the studies that did not reference previous work were lacking in their reporting of many aspects of our criteria suggesting the need for more comprehensive reporting of data collection and analysis methods within such studies.

>>>>

To determine the current state of methods reporting in the field we searched for papers from 2013 in 22 top colour science journals (_Animal Behaviour_, _Behavioral Ecology_, _Journal of Experimental Biology_, _Biology Letters_, _Proceedings of the Royal Society B: Biological Sciences_, _Biological Journal of the Linnean Society_, _Ethology_, _The American Naturalist_, _Ecology Letters_, _Journal of Evolutionary Biology_, _American Journal of Botany_, _Ecology and Evolution_, _Oikos_, _Ecology_, _Journal of Ecology_, _Behavioral Ecology and Sociobiology_, _Current Zoology_, _Naturwissenschaften_, _New Phytologist_, _PLoS ONE_, _Evolution_, _Functional Ecology_). For each of the journals, we used the Boolean search terms 'colour*', 'color*' or 'spectra*' and searched for these in the title or abstract from each of the journal home pages. We read the titles and abstracts of each paper and included only those papers that explicitly used either a spectrophotometer or camera to quantify colour signals. We excluded papers that were: 1) review papers; 2) methodological papers; 3) papers quantifying colour patterns rather than the chromatic properties of a colour patch; and 4) papers taking microspectrophotometric measurments of retinal absorbance. To review the large number of papers returned from the searches, journals were haphazardly divided up between the authors. In order to reduce the risk of observer bias in our scoring, papers were read and reassessed by a total of three authors. Any discrepancies between the assessor scores were discussed and agreed upon prior to analysis. We then tabulated what details of the methods were reported against our criteria. The data along with analysis script can be found at: https://github.com/daniel1noble/colsci_rep (TODO: GIVE IT A DOI?). We have kept the papers used in our dataset annoymous to avoid accusing specific colleagues of inadvertant reporting. We feel that the issue of reporting is something attributable to the ambiguity and lack of guidelines in our field and not something specific to individual research groups.

@@

While some of the percentages reported above seem alarming, it is important to note that papers often made reference to previous work for various methods (`r round(ref_stud, digits = 2)`%), so these figures are slightly liberal given that referenced work may have comprehensively covered some of these criteria. Despite this, many of the studies that did not reference previous work were lacking in their reporting of many aspects of our criteria suggesting the need for more comprehensive reporting of data collection and analysis methods within such studies.
